---
title: " "
output:
  pdf_document:
    number_sections: TRUE
geometry: "left = 2.5cm, right = 2cm, top = 2cm, bottom = 2cm"
fontsize: 11pt
header-includes:
  - \usepackage{float}
  - \usepackage{sectsty}
  - \usepackage{paralist}
  - \usepackage{setspace}\spacing{1.5}
  - \usepackage{fancyhdr}
  - \usepackage{lastpage}
  - \usepackage{graphicx}
  - \usepackage{dcolumn}
  - \usepackage{tabularx}
  - \usepackage{hyphenat}
  - \usepackage{natbib}\bibliographystyle{agsm}
  - \usepackage[nottoc, numbib]{tocbibind}

bibliography: bibliography.bib
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "tese") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```

\allsectionsfont{\centering}
\subsectionfont{\raggedright}
\subsubsectionfont{\raggedright}

\pagenumbering{gobble}


 \begin{titlepage}
    \begin{center}
      \hspace{-1cm}
      \begin{minipage}[t]{0.125\linewidth}
        \includegraphics[height=7em]{fig/logo_univ.pdf}
      \end{minipage}      
      \hspace{0.1cm}
      \begin{minipage}[t]{0.73\linewidth}
        \begin{center}
          \vspace{-5.5em}
          \textbf{\large Universidade Federal da Bahia}\\
          \vspace{0.4em}%
          \textbf{\large Faculdade de Medicina}\\ 
          \vspace{0.4em}
          \textbf{\small Programa de Pós-Graduação em Ciências da Saúde}
        \end{center}
      \end{minipage}      
    \hspace{0.1cm}
      \begin{minipage}[t]{0.125\linewidth}
        \includegraphics[height=7.5em]{fig/logo_fac.pdf}
      \end{minipage}\\
    \end{center}
  \vspace{2.05cm}
  \begin{center}
    \MakeUppercase{\bf Titulo}\par
  \vspace*{4cm}
  \begin{flushright}
  {\bf Thiago Cerqueira Silva}
  \end{flushright}
  \vspace{4cm}
  \textbf{Doutorado\ de\ XXXX }
  \end{center}
  \vspace*{2.1cm}
  \vspace*{\fill}
  \begin{center}
  \vspace{1.5 cm}
  \normalsize
  mm yy
  \end{center}
\end{titlepage}

<!-- SContra capa -->
  \begin{titlepage}
    \begin{center}
      \hspace{-1cm}
      \begin{minipage}[t]{0.125\linewidth}
        \includegraphics[height=7em]{fig/logo_univ.pdf}
      \end{minipage}      
      \hspace{0.1cm}
      \begin{minipage}[t]{0.73\linewidth}
        \begin{center}
          \vspace{-5.5em}
          \textbf{\large Universidade Federal da Bahia}\\
          \vspace{0.4em}
          \textbf{\large Faculdade de Medicina da Bahia}\\
          \vspace{0.4em}
          \textbf{\small Programa de Pós-Graduação em Ciências da Saúde}
        \end{center}
      \end{minipage}      
    \hspace{0.1cm}
      \begin{minipage}[t]{0.125\linewidth}
        \includegraphics[height=7.5em]{fig/logo_fac.pdf}
      \end{minipage}\\
    \end{center}
  \vspace{1.05cm}
  \begin{center}
      \MakeUppercase{\bf Título}\par
  \vspace*{3cm}
  \nohyphens{{Thiago}\ {Cerqueira Silva}}\par
  \end{center}
  \vspace*{2.1cm}
  \begin{flushright}
  \begin{minipage}{8.45cm}
  {Tese de Doutorado apresentada ao programa de Pós-Graduação em Ciências da Saúde, 
Faculdade de Medicina da Bahia, da Universidade Federal da Bahia, como parte dos 
requisitos necessários à obtenção do título de Doutor em Ciências da Saúde.}\par
  \vspace*{7.5mm}
  Orientadores: \par
  Viviane
  \end{minipage}\par
  \end{flushright}
  \vspace*{\fill}
  \begin{center}
  \vspace{1.5 cm}
  \normalsize
  mm yy
  \end{center}
\end{titlepage}
  

\newpage

\pagenumbering{gobble}

\begin{centering}

{\bf Abstract}

\end{centering}

\spacing{1.5}

(the spacing is set to 1.5)

no more than 250 words for the abstract

- a description of the research question/knowledge gap – what we know and what we don’t know
- how your research has attempted to fill this gap
- a brief description of the methods
- brief results
- key conclusions that put the research into a larger context

\pagenumbering{roman}

\newpage

\centering
\raggedright
\newpage
\tableofcontents

\newpage

```{r acknowledgments, child='acknowledgments.Rmd'}
```

\newpage

```{r intro, child = 'introduction.Rmd'}
```
\pagenumbering{arabic}

\newpage

```{r methods, child = 'methods.Rmd'}
```

\newpage

```{r results, child = 'results.Rmd'}
```

\newpage

```{r discussion, child = 'discussion.Rmd'}
```

\newpage

```{r conclusion, child = 'conclusion.Rmd'}
```

\newpage

```{r biblio, child = 'bibliography.Rmd'}
```

\newpage

```{r appendix, child = 'appendix.Rmd'}
```